TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
captions

%---------------------------
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/demo_derivatives_teff1.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff2.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff3.png}
\end{center}
\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallcities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463 K$}. \label{fig:demo_teff}
\end{figure}

%---------------------------
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/demo_derivatives_feh1.png}
\includegraphics[width=16cm]{figures/demo_derivatives_feh2.png}
\includegraphics[width=16cm]{figures/demo_derivatives_feh3.png}
\end{center}
\caption{\textit{Top two panels of each plot:} Mann-trained model for varying metallicities and similar temperatures. \textit{Third panel:} Derivative of \thecannon\ model with respect to metallicity, taken at the median training metallicity, [Fe/H]$=-0.03$.} \label{fig:demo_feh}
\end{figure}

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{Validation test \label{fig:aspcap_cannon_validation}}
\end{figure}

>>>>

%---------------------------
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/demo_derivatives_teff1.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff2.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff3.png}
\end{center}
\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallcities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K}. \label{fig:demo_teff}
\end{figure}

%---------------------------
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/demo_derivatives_feh1.png}
\includegraphics[width=16cm]{figures/demo_derivatives_feh2.png}
\includegraphics[width=16cm]{figures/demo_derivatives_feh3.png}
\end{center}
\caption{\textit{Top two panels of each plot:} Mann-trained model for varying metallicities and similar temperatures. \textit{Third panel:} Derivative of \thecannon\ model with respect to metallicity, taken at the median training metallicity, [Fe/H]$=-0.03$ dex.} \label{fig:demo_feh}
\end{figure}

@@

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{Validation test of \cannon\ temperatures (left), as compared to \aspcap\ temperatures (right) using three different color-temperature relations derived from \citealt{Mann:2015}, \citealt{Casagrande:2008}, and \citealt{Boyajian:2013}. For all three relations  \label{fig:aspcap_cannon_validation}}
\end{figure}
